---
title: "Positive peace at varying levels of violence"
output:
  pdf_document: default
  html_notebook: default
---


```{r echo = F, results = 'hide', warning=F, message=F}

library('ProjectTemplate')
purrr::quietly(load.project(override.config = list(data_loading =F)))


df = rio::import("S:/Institute for Economics and Peace/Research/Research Briefs/Positive Peace/Positive Peace Systems/Correlations/results-correlations-2018-internalpeace.xlsx",
                 which = 2)

tmp = df %>% 
  gather("group", "r", -c(names(df)[c(1:5)])) %>%
  mutate(r = as.numeric(r)) %>% 
  filter(!is.na(r)) %>% 
  group_by(category, group) %>%
  top_n(3, abs(r))


```


Previous research suggests that different aspects of positive peace (PP) are most valuable at different levels of negative peace (NP).

One possible method to observe this is to examine the correlations between PP indicators and internal peace in a group-wise fashion, looking at the specific correlations for highly peaceful countries, medium peace countries and less peaceful countries. 

As an initial exploratory analysis, this has been done using subsets of 60 countries at a time, based on their internal peace rank. Figure 1 gives an example using indicators that have been categorized within Well-Functioning Government.


```{r, echo = F, fig.pos = "!", fig.cap= "WFG Correlates by internal peace rank, 2018"}
x = "pp-wfg"

pp = tmp %>% 
  filter(category == x, group != "corall")

pp$variablename1 = factor(pp$variablename1, rev(unique(pp$variablename1)), ordered = T)

pp$group = gsub("cor", "Rank ", pp$group)

p <- ggplot(pp, aes(x = group, y = variablename1, size = abs(r))) +
  geom_point() + theme_minimal() + theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(axis.text.y = element_text(size = 7),
        axis.text.x = element_text(size = 7),
        plot.title = element_text(hjust = 0, size = 9)) +
  labs(y = "", x = "")

p 

```




