---
title: \textbf {Positive peace at varying levels of negative peace}

output:
  pdf_document: default
  html_notebook: default
---


```{r echo = F, results = 'hide', warning=F, message=F}

library('ProjectTemplate')
purrr::quietly(load.project(override.config = list(data_loading =F)))


df = rio::import("S:/Institute for Economics and Peace/Research/Research Briefs/Positive Peace/Positive Peace Systems/Correlations/results-correlations-2018-internalpeace.xlsx",
                 which = 2)

tmp = df %>% 
  gather("group", "r", -c(names(df)[c(1:5)])) %>%
  mutate(r = as.numeric(r)) %>% 
  filter(!is.na(r)) %>% 
  group_by(category, group) %>%
  top_n(3, abs(r))


```


Previous research suggests that different aspects of positive peace (PP) are most valuable at different levels of negative peace (NP).

One possible method to observe this is to examine the correlations between PP indicators and internal peace in a group-wise fashion, looking at the specific correlations for highly peaceful countries, medium peace countries and less peaceful countries. 

As an initial exploratory analysis, this has been done using subsets of 60 countries at a time, based on their internal peace rank. Figure 1 gives an example using indicators that have been categorized within Well-Functioning Government. The chart shows the top 3 correlates for each group of countries.

```{r, echo = F, fig.pos = "H", fig.fullwidth = T, fig.cap= "WFG Correlates by internal peace rank, 2018"}
x = "pp-wfg"

pp = tmp %>% 
  filter(category == x, group != "corall")

pp$variablename1 = factor(pp$variablename1, rev(unique(pp$variablename1)), ordered = T)

pp$group = gsub("cor", "Rank ", pp$group)

p <- ggplot(pp, aes(x = group, y = variablename1, size = abs(r))) +
  geom_point() + theme_minimal() + theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(axis.text.y = element_text(size = 7),
        axis.text.x = element_text(size = 7),
        legend.text = element_text(size = 7),
        axis.title.x=element_blank(),
        axis.title.y=element_blank()) +
  labs(y = "", x = "")

p 

```


We can see that the data visualization is useful, but more work is required. 

1. Some of the variables are already IEP composite scores (Well-Functioning Government, etc) and need to be removed manually


```{r, echo = F, fig.pos = "H", fig.fullwidth = T, fig.cap= "WFG Correlates by internal peace rank, 2018"}

source("./munge/01 set up df.R")

x = "pp-wfg"

pp = tmp %>% 
  filter(category == x, group != "corall")

pp$variablename1 = factor(pp$variablename1, rev(unique(pp$variablename1)), ordered = T)

pp$group = gsub("cor", "Rank ", pp$group)

p <- ggplot(pp, aes(x = group, y = variablename1, size = abs(r))) +
  geom_point() + theme_minimal() + theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(axis.text.y = element_text(size = 7),
        axis.text.x = element_text(size = 7),
        legend.text = element_text(size = 7),
        axis.title.x=element_blank(),
        axis.title.y=element_blank()) +
  labs(y = "", x = "")

p 

```




